Terms are used in very specific manner in the documentation and in both the
client and the server, therefore it is really essential to understand their
meaning. Otherwise, it is possible to misunderstand the rest of the text.

\comment[anyone]{Petr}{check if this makes sense!}
\begin{description}
\item[Document]
The document is an arbitrary text that is processed by \textan{}. E.g. a police
report, a letter, a movie review or a judgment. In the following text the terms
document and report are used interchangeably.

\item[Object]
The term "object" refers to our representation of some unique thing in
\textan{}. Consider for example a person with name Joseph Smith from Prague with
identifier 000123/4567. The object refers to this person in the real world, in
meat and bones.

\item[Alias]
The alias represents a designation of a object. For example: Joseph Smith, Joe
Smith, Joey S., J. Smith or just Smith can be names of one concrete person.
Names are aliases for the person.

\item[Entity]
An entity is a sequence of words recognized either by a named entity recognizer
or by a user. The entity will be later assigned to an object. Consider for example
the sentence: Joe Smith was seen in Prague on 5th September. The sentence contains
3 entities: Joe Smith (person), Prague (city), 5th September (date). We don't know
which objects belong to these entities yet. Prague can represent the capital city
of the Czech Republic, or a city in the USA.

\item[Object/Entity Type]
Each object and each entity has a type. For example person, date, city, country
etc. The set of types in the system depends on the domain which the system is
deployed to. There are some universal predefined \comment[author of this sentence]{Petr}{Really? Where? I don't know about any predefined type!} ones, but the system
administrator needs to prepare a customized list to fully unleash the power of
the project. \comment[Petr]{Petr}{Rewrite this paragraph}

\item[Object Assignment]
\comment{Petr}{Need check.}
A Object assignment (or just assignment) is a process at which is some object
assigned to some entity.  After assignment, the text that represents an entity
in a document becames an alias of the assigned object. An entity and an assigned
object must have a same type, this is an essential aspect of the assignment.
For example, there is a document in which was found an entity of type "date" with
text "14th March 2011" and an object of type "date" that represents a day with
aliases "the Fourteenth of March, 2011", "14/3/2011" and "14/3/11". The object will
be probably assigned to the entity, because we know that they represents same thing.
After assignment, the object will have also the alias "14th March 2011".

\item[Alias Occurrence]
\comment[Petr]{Petr}{Description of alias occurence}

\item[Object Merging]
Because objects are based only on information from documents, there may be a situation
in which two objects represent same thing. The operation "merge object" is used
to solve this situation, it merge two object into one and original objects are
replaced with the new object. The new object has aliases of both original objects.
A reverse operation is called "split objects".

\item[Relation]
The relation represents any relationship between objects mentioned in a document.
A relation can be represented in a document by an anchor word, or it can be
unexpressed, which means without any anchor in a document. See Anchor below.
Consider this example: "Adam (890524/1367) is married to Eve". Three objects
appear in the sentence - persons Adam and Eve and the id 890524/1367. There
are two relations: Adam "has" 890524/1367 without an anchor and Adam "marriage"
Eve with the anchor "married".

\item[Relation Type]
Each relation has a type. For example born, reside, die, kill etc. Similarly to
object/relation types the set of relation types in the system depends on the
domain which the system is deployed to. There are some universal predefined \comment[author of this sentence]{Petr}{Really? Where? I don't know about any predefined type!}
ones, but the system administrator needs to prepare customized list to fully 
unleash the power of the project. \comment[Petr]{Petr}{Rewrite this paragraph}

\item[Anchor]
An anchor is a word or a sequence of words that is bound to a relation between
objects. Consider for example the sentence: Joey Smith killed Mary-Ann S. There
is a relation between Joey Smith and Mary-Ann S., which is represented by the
word "killed". The word is the anchor.
\comment{Ondrej}{Why do you not write about type here?}
\comment{Petr}{The example should show what is an anchor. A type isn't important in this situation.}

\item[Roles and orders]
Each object in a relation can have a role assigned. This role is mostly used
for visualisation and storing additional information. Moreover object can also
have order assigned which is just an integral number used for graph
visualization\ifdefined\USRDOC{} (see Section \ref{sssec:EditRelations})\fi{}
\ifdefined\DEVDOC{} (see Section \ref{USR-sssec:EditRelations} in the user
documentation)\fi{}. For example relation created from sentence
"Bill killed Joe." could be represented like this:
Bill (-1, murderer) --kill--> (1, victim) Joe.
\end{description}

