\documentclass[12pt,a4paper]{report}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

\usepackage{geometry}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage[some]{background}
\usepackage{listings}
\usepackage{footmisc}

%TODO select color coresponding to logo
\definecolor{titlepagecolor}{cmyk}{1,.60,0,.40}
\definecolor{javagreen}{rgb}{0.25,0.5,0.35}

\backgroundsetup{
scale=1,
angle=0,
opacity=1,
contents={
\begin{tikzpicture}[remember picture,overlay]
  \path [fill=titlepagecolor] (current page.west)rectangle (current page.north east); 
  \draw [color=white, very thick] (5,0)--(5,0.5\paperheight);
 \end{tikzpicture}}
}

\DeclareFixedFont{\bigsf}{T1}{phv}{b}{n}{1.5cm}

\usepackage[unicode,colorlinks=true]{hyperref}
\hypersetup{pdftitle=TextAn - user documentation}
\hypersetup{pdfauthor={Petr Fanta, Duc Tam Hoang, Adam Huječek, Václav Pernička, Jakub Vlček}}
\hypersetup{linkcolor=black, citecolor=black, urlcolor=black, filecolor=black}

\makeatletter
\def\@makechapterhead#1{
  {\parindent \z@ \raggedright \normalfont
   \Huge\bfseries \thechapter. #1
   \par\nobreak
   \vskip 20\p@
}}
\def\@makeschapterhead#1{
  {\parindent \z@ \raggedright \normalfont
   \Huge\bfseries #1
   \par\nobreak
   \vskip 20\p@
}}
\makeatother

\def\chapwithtoc#1{
\chapter*{#1}
\addcontentsline{toc}{chapter}{#1}
}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\lstdefinelanguage{properties}{% new language for listings
  basicstyle=\ttfamily,
  sensitive=false,
  morecomment=[l]{\#},      % comment
  morestring=[b]",          % string def
  commentstyle=\color{javagreen},
  basicstyle=\small
}

\setkeys{Gin}{resolution=96}

\newcommand{\textan}{\emph{TextAn}}

\begin{document}

%TODO better titlepage
\begin{titlepage}
\BgThispage

\newgeometry{left=2cm,right=6cm,bottom=2cm}
\vspace*{0.3\textheight}
\noindent
\textcolor{white}{\bigsf TextAn}

\vspace*{1cm}
\noindent
\textcolor{white}{\Huge\textbf{\textsf{User Documentation}}}

\vspace*{2cm}\par
\noindent
\begin{minipage}{0.35\linewidth}
\textbf{Authors} \\
Petr Fanta \\
Duc Tam Hoang \\
Adam Huječek \\
Václav Pernička \\
Jakub Vlček\vspace{40pt} \\
\textbf{Supervisor} \\
Ondřej Bojar\vspace{40pt} \\
\textbf{Version} \\
0.1\vspace{40pt} \\
\textbf{Date} \\
\today \\
\end{minipage}

%TODO add logo

\end{titlepage}
\restoregeometry

\pagenumbering{roman}
\tableofcontents

%\chapter*{Intro}
%\addcontentsline{toc}{chapter}{Intro}


\chapter{User Guide}
\pagenumbering{arabic}

\section{Introduction}

TODO what is textan

TODO basic usage

\subsection{System overview}


\subsection{Glossary}

TODO definitions of terms in documentation and applications

\subsection{Conventions} %is this section needed?



\chapter{Administrator guide}

%TODO client instalation guide in the administrator guide or user guide?

\section{Server}

\subsection{Installation guide}


This section will show you how to install and build \textan\ server. 
%An installation guide for a server side application of \textan.

\subsubsection{Prerequisites}
\label{sssec:SerInstPre}

The \textan\ server requires installation of \emph{Java 8 JRE
\footnote{We recommend to use JRE from \emph{Oracle}, available at: \url{http://www.oracle.com/technetwork/java/javase/downloads/index.html}}}
or a later version and a relational database system (e.g. \emph{MySQL}).
The server should be platform independent, so it runs on any system where JRE is available,
but it depends on native and 3rd party libraries. 
Supported operating systems in the distribution of the \textan\ server are
Linux (32 bit and 64 bit) and Windows (32 bit and 64 bit). % I am thinking ...

\subsubsection{Installation}

The \textan\ server distribution archive contains all files needed for \textan\ server to operate,
such as server binaries, native libraries, run scripts and additional resources.
For installation it is sufficient to unpack its content into any directory.

\subsubsection{Basic configuration}

Before the first start, it is necessary to set up the server and the database.

TODO write how to setup server

TODO add some link to \ref{sec:ServerSettings}

\subsubsection{Starting the server}

The server can be started by starting scripts in its root directory. 
Scripts for different operating systems unfortunately do not provide the same functionality.

The start script for the Linux-based operating system (\emph{run.sh}) runs the server application as daemon
and can be used to run the server as system service.

The start script for the Microsoft Windows OS is less powerful, only runs the server application. 
To run the server as a background process, the Windows Service is required. 
Unfortunately, there are no components shipped with the Jetty Distribution to make it a formal Windows Service.
However, we recommend the use of \emph{Apache ProcRun's Daemon
\footnote{More information can be found on \url{https://commons.apache.org/proper/commons-daemon/procrun.html} and in JavaDoc documentation for \emph{cz.cuni.mff.ufal.textan.server.AppEntry} class.}}.

\subsection{Settings}
\label{sec:ServerSettings}

\subsubsection{Web server settings}

%connector
\paragraph{server.connector.host} The particular interface to listen on. If not set or 0.0.0.0, the web server listens on port on all interfaces.

\paragraph{server.connector.port} The port to listen on. If not set, the web server listens on port 9500.

%thread pool
\paragraph{server.threadPool.maxThreads} The maximum number of threads in web server thread pool. It determines a maximum number of simultaneously opened connections. The default value is 200.

\paragraph{server.threadPool.minThreads} The minimum number of threads in web server thread pool. The default value is 8.

\paragraph{server.threadPool.idleTimeout} The time in milliseconds that the connection can be idle before it is closed.

\subsubsection{Database connection settings}

%jdbc
\paragraph{jdbc.driverClassName} 

\paragraph{jdbc.url} 

\paragraph{jdbc.user}

\paragraph{jdbc.pass}


%c3p0 (http://www.mchange.com/projects/c3p0/#configuration_properties)
\paragraph{c3p0.maxPoolSize}

\paragraph{c3p0.minPoolSize}

\paragraph{c3p0.initialPoolSize}

\paragraph{c3p0.acquireIncrement}

\paragraph{c3p0.maxIdleTime}

\paragraph{c3p0.checkoutTimeout}

\paragraph{c3p0.maxStatements}

\paragraph{c3p0.maxStatementsPerConnection}

\paragraph{c3p0.idleConnectionTestPeriod}

%hibernate
\paragraph{hibernate.dialect}

\paragraph{hibernate.show\_sql}

%NameTag
\subsubsection{Named entity recognizer settings}
This section is mainly about settings stored in NametagLearning.properties.
There are parameters for neural network which nametag use for learning and switches for nametag functions.
Also, there are settings for affecting models storing and learning data generating.
All inputs are assumed to be in UTF-8 encoding.


\paragraph{ner\_identifier}
Identifier of the named entity recognizer type. This affects the tokenizer used in this model, and in theory any other aspect of the recognizer. Supported values are:
\begin{description}
\item[$\cdot$] czech
\item[$\cdot$] english
\item[$\cdot$] generic
\end{description}

\paragraph{tagger}
Identifier of tagger. NameTag can utilize several taggers to obtain the tags and lemmas:

\begin{description}
\item[$\cdot$ trivial] Do not use any tagger. The lemma is the same as the given form and there is no part of speech tag.
\item[$\cdot$ external] Use some external tagger. The input "forms" can contain multiple tab-separated values, first being the form, second the lemma and the rest is part of speech tag. The part of speech tag is optional. The lemma is also optional and if missing, the form itself is used as a lemma.
\item[$\cdot$ morphodita:model] Use MorphoDiTa as a tagger with the specified model. This tagger model is embedded in resulting named entity recognizer model. The lemmatizer model of MorphoDiTa is recommended, because it is very fast, small and detailed part of speech tags do not improve the performance of the named entity recognizer significantly.
\end{description}

\paragraph{featuresFile}
Path of generated file, based on property file 
The recognizer utilizes feature templates to generate features which are used as the input to the named entity classifier. The feature templates are specified in a file, one feature template on a line. Empty lines and lines starting with \# are ignored.

The first space-separated column on a line is the name of the feature template, optionally followed by a slash and a window size. The window size specifies how many adjacent words can observe the feature template value of a given word, with default value of 0 denoting only the word in question.

List of commonly used feature templates follows. Note that it is probably not exhaustive (see the sources in the features directory).

\paragraph{stages}
The number of stages performed during recognition. Common values are either 1 or 2. With more stages, the model is larger and recognition is slower, but more accurate.

\paragraph{iterations}
The number of iterations performed when training each stage of the recognizer. With more iterations, training take longer (the recognition time is unaffected), but the model gets over-trained when too many iterations are used. Values from 10 to 30 or 50 are commonly used.

\paragraph{missing\_weight}
Default value of missing weights in the log-linear model. Common values are small negative real numbers like -0.2.

\paragraph{initial\_learning\_rage}
learning rate used in the first iteration of SGD training method of the log-linear model. Common value is 0.1.

\paragraph{final\_learning\_rage}
learning rate used in the last iteration of SGD training method of the log-linear model. Common values are in range from 0.1 to 0.001, with 0.01 working reasonably well.

\paragraph{gaussian}
The value of Gaussian prior imposed on the weights. In other words, value of L2-norm regularizer. Common value is either 0 for no regularization, or small real number like 0.5.

\paragraph{hidden\_layer}
Experimental support for hidden layer in the artificial neural network classifier. To not use the hidden layer (recommended), use 0. Otherwise, specify the number of neurons in the hidden layer. Please note that non-zero values will create enormous models, slower recognition and are not guaranteed to create models with better accuracy.

\paragraph{heldout\_data}
Optional parameter with heldout data in the described format. If the heldout data is present, the accuracy of the heldout data classification is printed during training. The heldout data is not used in any other way.

\paragraph{waiting\_time}
Maximum time for learning new model (only when learning is blocking - model doesn't exist)

\paragraph{default\_training\_data\_file}
Sample file with initial training data, which is copied before training data generated from database. When this property is empty, no default training data are used.

\paragraph{maximum\_stored\_models}
Number of maximum stored models. When limit is exceeded, the oldest models are deleted

\paragraph{form}
Size of window when forms are used as features (0 when are not used)

\paragraph{lemma}
Size of window when lemma ids are used as features (0 when are not used)

\paragraph{raw\_lemma}
Size of window when raw lemmas are used as features (0 when are not used)

\paragraph{raw\_lemma\_capitalization}
Size of window when capitalization of raw lemma is used as features (0 when are not used)

\paragraph{tag}
Size of window when tags are used as features (0 when are not used)

\paragraph{numeric\_time\_value}
recognize numbers which could represent hours, minutes, hour:minute time, days, months or years

\paragraph{czech\_lemma\_term}
feature template specific for Czech morphological system by Jan Hajič (Hajič 2004). The term information (personal name, geographic name, ...) specified in lemma comment are used as features.

\paragraph{brown\_clusters}size of window foe Brown clusters 

\paragraph{brown\_clusters\_file}
Use Brown clusters found in the specified file. An optional list of lengths of cluster prefixes to be used in addition to the full Brown cluster can be specified. Each line of the Brown clusters file must contain two tab-separated columns, the first of which is the Brown cluster label and the second is a raw lemma.

\paragraph{gazetteers}
Size of window when gazetteers are used (0 when are not used)

\paragraph{gazetteers\_directory}
Directory of gazetteers files. Each file is one gazetteers list independent of the others and must contain a set of lemma sequences, each on a line, represented as raw lemmas separated by spaces.

\paragraph{previous\_stage}
use named entities predicted by previous stage as features

\paragraph{email\_detector}
Detect URLs and emails. If an URL or an email is detected, it is immediately marked with specified named entity type and not used in further processing.

\subsection{Data formats}

\section{Client}

This section contains all information needed to successfully install, configure and run \textan\ client side application.
However thanks to \textan\ client-server architecture and extensive use of webservices,
it is easy to prepare own implementation in any programmer language desired or even use general solutions as SoapUI
\footnote{More information can be found at \url{http://www.soapui.org/}},
if \textan\ default client does not provide all required features, user experience or integration to legacy system is needed.

\subsection{Installation guide}

This section describes how to install and configure \textan\ client on workstations of end users.

\subsubsection{Prerequisites}

The \textan\ client has the same requirement for \emph{Java 8 JRE} or later as the server (see \ref{sssec:SerInstPre}).
However, unlike the server side, it is pure Java application so there are no other additional limitations for operating system etc.
Any platform where JRE 8 is available can support the client.

\subsubsection{Installation}

Unpack an archive with the \textan\ client distribution into any directory. 
The archive contains a .jar file and starting scripts for the \emph{Microsoft Windows} and Linux-based operating systems
\footnote{run.bat for MS Windows and run.sh for Linux clones.\label{runscript_note}}.

\subsubsection{Basic configuration}

If the client is not supposed to connect to the default server, it is necessary to configure a server location. 
The client settings are by default stored in \emph{TextAn.properties\footnote{A description of format of .properties file can be found at \url{http://en.wikipedia.org/wiki/.properties}}}
in the client directory. 
Simply edit or add following lines to properties file (create it if it does not exist),
replacing default server address with the actual one:
\begin{lstlisting}[frame=single,language=properties]
#url of the document processor
url.document=http://localhost:9500/soap/document
#url of the document processor wsdl
url.document.wsdl=http://localhost:9500/soap/document?wsdl
#url of the data provider
url.data=http://localhost:9500/soap/data
#url of the data provider
url.data.wsdl=http://localhost:9500/soap/data?wsdl
\end{lstlisting}

\subsubsection{Starting the client}

The .jar file from the distribution archive is executable,
but we recommend to use starting scripts\footref{runscript_note}.
Please consult documentation of your Java Platform provider,
if running scripts are not available for your system.
For description of command line arguments see \ref{ssec:CliCmdArg}

\subsubsection{Uninstallation}

The client application does not use any files or resources outside its install directory,
unless explicitly told to do otherwise.
To uninstall the client just delete its installation folder
and all files explicitly used as configuration storage.

\subsection{Settings}

This section describes all settings affecting the client behaviour.
The two basic means are command line arguments and configuration file in properties format.

\subsubsection{Command line arguments}
\label{ssec:CliCmdArg}

The client has one command line option (-h, --help, /H, /?) which displays the usage information.
Apart from that it takes only one command line argument which is the location of settings file.
If no file is specified, default property file \emph{TextAn.properties} will be used.
If '-' is provided, the standard input will be read and settings will not be stored.

\subsubsection{TextAn.properties}

This section contains a list of properties from configuration file that controls client behaviour.

%TODO: add all the properties and their description, can point to ssec:Settings

\subsection{Usage}

\subsubsection{First run}

\subsubsection{Working space}

\subsubsection{Settings}
\label{ssec:Settings}

\subsubsection{Report processing}

\subsubsection{Listing objects}

\subsubsection{Graph views}

\end{document}
